Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density

### 2018-05-28 manuscript.tex
Working on sect 3

With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respectively) , and present advantages and limitations for both of these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. 
The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.

@@

Exoplanets will only produce a variation in RV's induced by a pure Doppler-shift of stellar spectra. Stellar activity and in particular the presence of active regions on the photosphere of the star, on the contrary, does not produce a blueshift or redshift of the spectra, but creates spurious RV's signal by modifying the shape of the spectral lines. To track these changes in the shape of the line profile, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced by \citep{Figueira-2013}, which provide an information on the average width and asymmetry of the CCF. A strong correlation between the estimated set of RV's and one or more of these parameters provides an indication that the RV's are affected by stellar activity signals.

@@

While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM). The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
%    \label{fig:spotA}
%\end{figure*}
%%

@@

Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star. The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as SN GAMMA (black circles) or BIS SPAN (red triangles). In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.  We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RV's (Fig.~\ref{fig:se.soap.spot.planet}). Concerning the standard errors related to the RV's if a faculae is creating spurious signals, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$, when using SN mean RV and $0.8$ when using SN median RV. By using SN median RV we get standard errors $20\%$ smaller than using the Normal fit and its corresponding mean. Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable. Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF. Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller. Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.

>>>>

With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as SN mean RV and SN median RV, respectively), and present advantages and limitations for both of these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. 
The width of the SN, SN FWHM, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF is estimated by the $\gamma$ parameter.

@@

\xavier{Exoplanets only produce a pure RV signal. Stellar activity on the contrary, and in particular the presence of active regions on the stellar photosphere, does not produce a blueshift or redshift of the entire stellar spectra, but creates a spurious RV signal by modifying the shape of spectral lines. To track these variations in the shape of the spectral lines}, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF. A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals are affecting our measurements.

@@

While the parameters BIS SPAN and FWHM have already been introduced and used in several analysis \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, we propose in addition to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM). The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
%    \label{fig:spotA}
%\end{figure*}
%%

@@

Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star. The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles). In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.  We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RV's (Fig.~\ref{fig:se.soap.spot.planet}). Concerning the standard errors related to the RV's if a faculae is creating spurious signals, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$, when using SN mean RV and $0.8$ when using SN median RV. By using SN median RV we get standard errors $20\%$ smaller than using the Normal fit and its corresponding mean. Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable. Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF. Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller. Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
